PANCHANGE_descriptives

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
Removed ocir from correlation plot between imputed retro scores and unimputed prepan scores

```{r Correlation prep chunk}
# Select items for correlation matrix
prepan_retro_items <- c(
    "gad.sum_score_prepan",
    "gad.sum_score_retro", 
    "ocir.sum_score_prepan",
    "ocir.sum_score_retro",
    "phq.sum_score_prepan",
    "phq.sum_score_retro"
)

>>>>

```{r Correlation prep chunk}
# Select items for correlation matrix
prepan_retro_items <- c(
    "gad.sum_score_prepan",
    "gad.sum_score_retro", 
    "phq.sum_score_prepan",
    "phq.sum_score_retro"
)
